---
name: John K.
surname: Best
position: "Graduate Research Assistant"
address: "Quantitative Ecology & Resource Management, University of Washington"
phone: +1 315 440 8420
www: www.posdefecology.net
email: "jkbest@uw.edu"
twitter: isposdef
github: jkbest2
orcid: 0000-0002-8920-0900
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
library(rorcid)

myorcid <- "0000-0002-8920-0900"
```

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "BS Biology & Physics", "September 2004 - May 2008", "Clarkson University", "Potsdam, NY",
  "MS Statistics", "August 2014 - May 2016", "University of Fairbanks", "Fairbanks, AK",
  "PhD Quantitative Ecology & Resource Management", "August 2016 - ", "University of Washington", "Seattle, WA"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Publications

```{r}
bibliography_entries("works.bib") %>%
  arrange(desc(author$family), issued)
```

# Funding

```{r}
tribble(
  ~ Title, ~ Year, ~ Grant, ~ Amount,
  "Improving spatiotemporal indices of abundance with fishery-dependent and -independent data", "2019 - 2022", "NMFS-Sea Grant Joint Fellowship in Population and Ecosystem Dynamics", "$120,000"
) %>%
  detailed_entries(Title, Year, Grant, Amount)
```

# Service

- Served as peer reviewer for *Fisheries Research*, *ICES Journal of Marine
  Sciences*, *Progress in Oceanography*, and *Aquatic Ecology*
- Co-organizer of the 2022 University of Washington College of the Environment
  Research Derby
- Co-organizer of the University of Washington Department of Statistics
  Spatiotemporal Reading Group

# Talks

```{r}
tribble(
  ~ Title, ~ Date, ~ Conference, ~ Where,
  "Fishery-dependent data in a spatiotemporal context", "March 28, 2018", "CAPAM Spatio-temporal modelling mini-workshop", "La Jolla, CA",
  "Standardizing spatially explicit fishery catch data", "July 5, 2018", "International Statistical Ecology Conference 2018", "St. Andrews, Scotland",
  "Nonstationarity in spatiotemporal fisheries models", "July 30, 2018", "Joint Statistical Meeting 2018", "Vancouver, WA",
  "Reparameterizing Bayesian state-space models for more reliable fits", "November 13, 2018", "Think Tank", "Seattle, WA",
  "Combining Fishery-independent and -dependent observations in a single index of abundance", "October 29, 2019", "Think Tank", "Seattle, WA",
  "Parameterizations for Bayesian state-space surplus production models", "November 14, 2019", "SAFS Graduate Student Symposium", "Seattle, WA",
  "Catchability as a spatiotemporal random effect for standardizing fishery-dependent data", "November 12, 2020", "SAFS Graduate Student Symposium", "Seattle, WA",
  "An index of abundance combining fishery-independent and -dependent observations allowing for spatially varying catchability", "July 16, 2021", "Statistics 2021 Canada", "Montreal, Canada (v)",
  "An index of abundance combining fishery-independent and -dependent observations allowing for spatially varying catchability", "September 21, 2021", "World Fisheries Conference 2021", "Adelaide, Australia (v)",
  "Spatially varying catchability for indices of abundance that include fishery-dependent data", "November 4, 2021", "SAFS Graduate Student Symposium", "Seattle, WA",
  "Spatially varying catchability for indices of abundance that include fishery-dependent data", "December 2, 2021", "2022 Sea Grant-NMFS Fellowship Symposium", "(v)"
) %>%
  detailed_entries(Title, Date, Conference, Where)
```
